\begin{absolutelynopagebreak}
\cvsection{Research activities, talks and scientific popularisation}
\begin{cvhonors}
  \cvhonor
	{AI Lab for Human and Social Sciences}
    {presentation at the kick-off conference of the AI Lab for Human and Social Sciences at the Centre d'Économie de la Sorbonne: "Automatic Classification of News Subjects in Broadcast News: Application to a Gender Bias Representation Analysis".}
    {Paris, France}
    {2024}
  \cvhonor
    {FIAT/IFTA world conference}
    {presentation at the International Federation of Television Archives (IFTA): "LLMs in practice: large-scale topic classification of audiovisual news".}
    {Bucharest, Romania}
    {2024}
  \cvhonor
    {JSALT 2023 Workshop \& Plein Champ Festival}
    {help in the organisation of the 2023 JSALT workshop which took place in Le Mans. In this context, scientific popularisation of the event with secondary school students and artist \textsc{Sarah Lembo} at the \textit{Plein Champ} festival.}
    {Le Mans, France}
    {2023}
 \cvhonor
    {JSALT 2022 Workshop}
    {involvement inside the Esperanto team (EU H2020 grant \textit{101007666}). Multilingual speech translation for under-resourced languages.}
    {Baltimore, USA}
    {2022}
  \cvhonor
    {Frederick Jelinek Memorial Summer Workshop}
    {attented the <<\textit{Eighth Frederick Jelinek Memorial Summer Workshop}>> at Johns Hopkins University. Involvement in the organisation of a Lab Work on biometric authentification and speech synthesis (3h30).}
    {Baltimore, USA}
    {2022}
  \cvhonor
    {IVADO/MILA Winter School}
    {attented the Winter <<\textit{Deep Learning School}>>, organised by IVADO and MILA. Financing by a RFI Atlanstic 2020 grant.}
    {online}
    {2021}
\cvhonor
    {European Researchers' Night}
    {organisation and scientific popularisation at LIUM stand on Artificial Intelligence.}
    {Le Mans, France}
    {2021, 2022}
\cvhonor
    {Fête de la Science}
    {conception and presentation of demonstration tools on Artificial Intelligence.}
    {Le Mans, France}
    {2021, 2022}
\end{cvhonors}
\end{absolutelynopagebreak}
